Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification

### 2019-07-23 190410_Paper_ACPR/paper_v2.tex
paper_acpr: submit abstract

% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v2}
    \caption{Structure of the network} \label{fig1}
\end{figure}

@@

% Dataset
\subsubsection{Dataset}
 In order to evaluate the verification performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used. Wi-Fi CSI dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) each signal is size of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas). Since the Wi-Fi signature signals in CSI packets in 2.4Ghz has firmware issues in their phase \cite{wang2015understanding}. we used only absolute value.

 % pre-processing
 Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy. Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action. Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals. As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the network.

@@

\subsubsection{1) Performance Evaluation}
% performance evaluation
The porposed method is evaluated under comparision of the proposed method with other verification methods based on verification accuracy.
verification performance is compared with existing linear methods in literature such as LSE, SVM and TER. Moreover, proposed method is compared by ConvNet based Siamese networks,we used same ConvNet model for our proposed method and Siamese network.

>>>>

% Figure 1
\begin{figure}
    \includegraphics[width=\textwidth]{fig1_tcnn_kar_v3}
    \caption{Structure of the network} \label{fig1}
\end{figure}

@@

% Dataset
\subsubsection{Dataset}
 In order to evaluate the verification performance of proposed system, Wi-Fi CSI signature dataset from \cite{moon2017air} was used. Wi-Fi CSI dataset consists of 2000 Wi-Fi CSI signature signals (4 directions $\times$ 50 identities $\times$ 10 samples) each signal is size of (500 packets $\times$ 30 subcarriers $\times$ 6 antennas). We used only the absolute value of a complex CSI signal since the 2.4Ghz Wi-Fi CSI signals has device firmware issues in their phase signal\cite{wang2015understanding}.

 % pre-processing
 Since every Wi-Fi signature signal has different data size, we firstly adopted the gradient operation with respect to the time instance to measure the short time energy. Data points with the highest short-time energy within the time period are then manually selected as the starting and the ending points of the in-air signature action. Subsequently, the Fast Fourier Transform based re-sampling method \cite{moon2017air} is implemented to unify the length of the signals. As a result, three-dimensional Wi-Fi signature signals with unified data size are obtained as the input of the ConvNet structure in the triplet network.

@@

\subsubsection{1) Performance Evaluation}
% performance evaluation
The porposed method is evaluated with other methods based on verification accuracy.
verification performance is compared with existing linear methods in literature such as Least Square Estimation(LSE), Support Vector Machine(SVM) and Total Error Rate(TER) minimization\cite{toh2008between}. Moreover, proposed method is compared by Siamese network\cite{koch2015siamese} and varlinna Triplet network\cite{hoffer2015deep} without mining, which are ConvNet based deep learning structure. We used same ConvNet structure for our proposed method and compared deep learning structure.
